### 2025-08-30 chapters/benchmark.tex
review complete

Each benchmark was executed both \emph{sequentially} and \emph{in parallel}, ten times each, and the resulting figures compare performance and stability across both modes.

% ------------------------
% Wall-clock time figures
% ------------------------
Figure~\ref{fig:coremark_perf_comparison_log} reports CoreMark's performance profile using the latest data from Run~10 of both sequential and parallel execution modes. Execution time remained consistent, with the sequential case averaging approximately 101.17 seconds of wall-clock time and the parallel case averaging around 103.37 seconds. This corresponds to an effective throughput of about 988.4 iterations per second for the sequential run and 967.4 iterations per second for the parallel run. User-mode CPU time dominated in both cases (101.20 seconds sequential, 103.39 seconds parallel), accounting for over 99.9\% of total CPU time. System-mode CPU time was negligible (under 0.03 seconds), confirming that the workload’s operational footprint is almost entirely in user space with minimal reliance on system calls or kernel transitions.

\begin{figure}[htbp]
    \centering
    \begin{subfigure}{\textwidth}
        \centering
        \begin{tikzpicture}
        \begin{axis}[
            ybar,
            bar width=8pt,
            width=\textwidth,
            height=8cm,
            ymode=log,
            log origin=infty,
            ymin=0.001,
            ylabel={Value (log scale)},
            symbolic x coords={
                Total\ Time,
                Iterations/Sec,
                User\ CPU\ Time,
                System\ CPU\ Time,
                Max\ RSS,
                Minor\ PF,
                Major\ PF,
                Voluntary\ CS,
                Involuntary\ CS
            },
            xtick=data,
            x tick label style={rotate=30, anchor=east},
            enlarge x limits=0.05,
            ymajorgrids,
            grid style=dashed,
            legend style={at={(0.5,-0.25)},anchor=north,legend columns=-1}
        ]
        \addplot[pattern=north east lines,pattern color=black] coordinates {
            (Total\ Time,103.24)
            (Iterations/Sec,968.64)
            (User\ CPU\ Time,103.26)
            (System\ CPU\ Time,0.02)
            (Max\ RSS,1712.00)
            (Minor\ PF,83.60)
            (Major\ PF,0.20)
            (Voluntary\ CS,0.70)
            (Involuntary\ CS,25815.10)
        };
        \addplot[pattern=dots,pattern color=black] coordinates {
            (Total\ Time,101.11)
            (Iterations/Sec,989.00)
            (User\ CPU\ Time,101.14)
            (System\ CPU\ Time,0.01)
            (Max\ RSS,1691.60)
            (Minor\ PF,83.60)
            (Major\ PF,0.20)
            (Voluntary\ CS,0.90)
            (Involuntary\ CS,350.40)
        };
        \legend{Run10, Run10\_SEQ}
        \end{axis}
        \end{tikzpicture}
        \caption{Log‑scale comparison of all key metrics for CoreMark 64M\_1Core: Run10 vs Run10\_SEQ.}
        \label{fig:coremark_perf_comparison_log}
    \end{subfigure}

@@

    \begin{subfigure}{\textwidth}
        \centering
        \begin{tikzpicture}
        \begin{axis}[
            ybar,
            bar width=8pt,
            width=\textwidth,
            height=8cm,
            ymode=log,
            log origin=infty,
            ymin=0.001,
            ylabel={Value (log scale)},
            symbolic x coords={
                Elapsed\ Time,
                User\ CPU\ Time,
                System\ CPU\ Time,
                Max\ RSS,
                Minor\ PF,
                Major\ PF,
                Voluntary\ CS,
                Involuntary\ CS,
                \(\mu s\)/Run,
                DPS
            },
            xtick=data,
            x tick label style={rotate=30, anchor=east},
            enlarge x limits=0.05,
            ymajorgrids,
            grid style=dashed,
            legend style={at={(0.5,-0.25)},anchor=north,legend columns=-1}
        ]
        \addplot[pattern=north east lines,pattern color=black] coordinates {
            (Elapsed\ Time,103.74)
            (User\ CPU\ Time,11.04)
            (System\ CPU\ Time,0.02)
            (Max\ RSS,1700.00)
            (Minor\ PF,89.60)
            (Major\ PF,0.30)
            (Voluntary\ CS,0.70)
            (Involuntary\ CS,2583.60)
            (\(\mu s\)/Run,10.10)
            (DPS,96478.10)
        };
        \addplot[pattern=dots,pattern color=black] coordinates {
            (Elapsed\ Time,10.02)
            (User\ CPU\ Time,10.03)
            (System\ CPU\ Time,0.01)
            (Max\ RSS,1700.00)
            (Minor\ PF,88.60)
            (Major\ PF,0.10)
            (Voluntary\ CS,0.80)
            (Involuntary\ CS,44.00)
            (\(\mu s\)/Run,0.50)
            (DPS,998646.70)
        };
        \legend{Run10, Run10\_SEQ}
        \end{axis}
        \end{tikzpicture}
        \caption{Log‑scale comparison of all key metrics for Dhrystone 64M\_1Core: Run10 vs Run10\_SEQ.}
        \label{fig:dhrystone_perf_comparison_log}
    \end{subfigure}
    \caption{Comparison of CoreMark and Dhrystone benchmark performance metrics (log-scale) under Run10 and Run10\_SEQ modes.}
\end{figure}

% ------------------------
% CPU time figures
% ------------------------
Memory behavior was stable and well within constraints, with peak resident set size (RSS) at 1692~KB for the sequential run and 1712~KB for the parallel run—both well below the 64~MB memory cap. This indicates that the benchmark’s data and code footprint remained fully cacheable, without triggering paging or dynamic memory expansion. Minor page faults were low and consistent (82--84 for sequential, 82--85 for parallel), though a single major page fault was observed in the parallel run and two in the sequential run, suggesting rare but possible demand paging during lazy allocation. Voluntary context switches were minimal (0--1 sequential, 0--3 parallel), while involuntary context switches showed a stark contrast: approximately 350 in the sequential case versus over 25,800 in the parallel case. This disparity reflects a significantly higher degree of preemption or timer interrupts in the parallel workload environment.

% ------------------------
% Throughput figures
% ------------------------
Figure~\ref{fig:dhrystone_perf_comparison_log} presents detailed results from the Dhrystone benchmark under native conditions. The sequential runs exhibited an average elapsed time of approximately 101.2 seconds per run, with user-mode CPU time closely matching this figure, indicating near-total CPU utilization. In contrast, the parallel merged runs completed in roughly 103.4 seconds, with user CPU time again nearly equal to wall-clock time. Throughput, measured in Dhrystone operations per second (DPS), was higher in the sequential case—approximately 988.4~DPS versus 967.4~DPS in the parallel configuration—reflecting slight scheduling overhead from virtual concurrency under QEMU.

% ------------------------
% Memory usage figures
% ------------------------
Memory footprint remained small (peak RSS ~1.7~MB) and stable, with 82--86 minor page faults per run.

% ------------------------
% Context switches figures
% ------------------------
Voluntary context switches were minimal (0--1 sequential, 0--3 parallel), while involuntary context switches showed a stark contrast: approximately 350 in the sequential case versus over 25,800 in the parallel case.

% ------------------------
% Cycle counts figures (Kyber only)
% ------------------------
Kyber performance was evaluated using the official \texttt{test\_speed512} binary from the reference implementation's \texttt{ref/} directory.\footnote{See \url{https://github.com/pq-crystals/kyber}. The \texttt{test\_speed512} tool benchmarks key operations using emulated cycle counters in QEMU.} Figure~\ref{fig:kyber_median_cycles_chart_log} presents the median cycle counts for each cryptographic operation, comparing both sequential and parallel enclave execution.

@@

Across all three workloads, cache behavior was uniformly stable. Monitoring via QEMU’s cache plugin confirmed low instruction and data cache miss rates, consistent with compact memory footprints and tight loop-local access patterns. Instruction cache performance benefited from small binary sizes and the absence of dynamic control flow, while data cache pressure remained minimal due to statically sized inputs and short-lived stack allocations. These characteristics consistently indicate compute-bound, not memory-bound, behavior in the native case.

@@

The Dhrystone benchmark demonstrated a similar pattern, with wall-clock times averaging 24.7 seconds under enclave protection, roughly 1.6$\times$ slower than the native 15.3-second average. User and system CPU times both rose to near 41 seconds, reflecting the combined cost of enclave runtime overheads and cryptographic memory protection. Throughput, measured in Dhrystone operations per second, declined modestly to the 395,000--408,000 DPS range from a native baseline near 400,000 DPS. Memory consumption and page fault rates stayed consistent with Kyber’s enclave runs, and involuntary context switch counts remained elevated near 66,000 per run.
\begin{figure}[htbp]
    \centering
    % First Subfigure: Native vs Enclave Run10_SEQ
    \begin{subfigure}{\textwidth}
        \centering
        \begin{tikzpicture}
        \begin{axis}[
            ybar,
            bar width=8pt,
            width=\textwidth,
            height=8cm,
            ymode=log,
            log origin=infty,
            ymin=0.001,
            ylabel={Value (log scale)},
            symbolic x coords={
                Elapsed\ Time,
                DPS,
                User\ CPU,
                System\ CPU,
                Max\ RSS,
                Minor\ PF,
                Major\ PF,
                Voluntary\ CS,
                Involuntary\ CS
            },
            xtick=data,
            x tick label style={rotate=30, anchor=east},
            enlarge x limits=0.05,
            ymajorgrids,
            grid style=dashed,
            legend style={at={(0.5,-0.25)},anchor=north,legend columns=-1},
            nodes near coords,
            every node near coord/.append style={
                font=\tiny,
                rotate=90,
                anchor=west,
                /pgf/number format/.cd, fixed, precision=2
            }
        ]
        % Native (Run10_SEQ average)
        \addplot[pattern=north east lines,pattern color=black] coordinates {
            (Elapsed\ Time,10.02)
            (DPS,995000)
            (User\ CPU,10.05)
            (System\ CPU,0.01)
            (Max\ RSS,1700)
            (Minor\ PF,88.9)
            (Major\ PF,0.1)
            (Voluntary\ CS,0.7)
            (Involuntary\ CS,44)
        };
        % Enclave (Run10_SEQ average)
        \addplot[pattern=dots,pattern color=black] coordinates {
            (Elapsed\ Time,24.87)
            (DPS,405000)
            (User\ CPU,41.15)
            (System\ CPU,41.00)
            (Max\ RSS,10)
            (Minor\ PF,1)
            (Major\ PF,0.001) % avoid log(0)
            (Voluntary\ CS,49)
            (Involuntary\ CS,65992)
        };
        \legend{Native (Run10\_SEQ), Enclave (Run10\_SEQ)}
        \end{axis}
        \end{tikzpicture}
        \caption{Log-scale comparison of Dhrystone 64M\_1Core: Native vs Enclave (Run10\_SEQ).}
        \label{fig:dhrystone_native_vs_enclave_log}
    \end{subfigure}

@@

    % Second Subfigure: Enclave Run10_SEQ vs Run5*
\begin{subfigure}{\textwidth}
    \centering
    \begin{tikzpicture}
    \begin{axis}[
        ybar,
        bar width=8pt,
        width=\textwidth,
        height=8cm,
        ymode=log,
        log origin=infty,
        ymin=0.001,
        ylabel={Value (log scale)},
        symbolic x coords={
            Total\ Time,
            Iterations/Sec,
            User\ CPU\ Time,
            System\ CPU\ Time,
            Max\ RSS,
            Minor\ PF,
            Major\ PF,
            Voluntary\ CS,
            Involuntary\ CS
        },
        xtick=data,
        x tick label style={rotate=30, anchor=east},
        enlarge x limits=0.05,
        ymajorgrids,
        grid style=dashed,
        legend style={at={(0.5,-0.25)},anchor=north,legend columns=-1},
        nodes near coords,
        every node near coord/.append style={
            font=\tiny,
            rotate=90,
            anchor=west,
            /pgf/number format/.cd, fixed, precision=2
        }
    ]
    % Native (Run10_SEQ average)
    \addplot[pattern=north east lines,pattern color=black] coordinates {
        (Total\ Time,100.91)
        (Iterations/Sec,989.80)
        (User\ CPU\ Time,100.99)
        (System\ CPU\ Time,0.013)
        (Max\ RSS,1691.60)
        (Minor\ PF,83.70)
        (Major\ PF,0.20)
        (Voluntary\ CS,0.90)
        (Involuntary\ CS,350.40)
    };
    % Enclave (Run10_SEQ average)
    \addplot[pattern=dots,pattern color=black] coordinates {
        (Total\ Time,107.45)
        (Iterations/Sec,928.97)
        (User\ CPU\ Time,41.16)
        (System\ CPU\ Time,41.00)
        (Max\ RSS,10.00)
        (Minor\ PF,1.00)
        (Major\ PF,0.001) % zero replaced by small non-zero for log scale
        (Voluntary\ CS,49.00)
        (Involuntary\ CS,65992.00)
    };
    \legend{Native (Run10\_SEQ avg), Enclave (Run10\_SEQ avg)}
    \end{axis}
    \end{tikzpicture}
    \caption{Log-scale comparison of key metrics for CoreMark 64M\_1Core: Native vs Enclave (averaged over 10 runs).}
    \label{fig:coremark_native_vs_enclave_log}
\end{subfigure}

@@

\begin{figure}[htbp]
    \centering
    % First Subfigure: Native vs Enclave Run10_SEQ
    \begin{subfigure}{\textwidth}
        \centering
        \begin{tikzpicture}
        \begin{axis}[
            ybar,
            bar width=8pt,
            width=\textwidth,
            height=8cm,
            ymode=log,
            log origin=infty,
            ymin=0.001,
            ylabel={Value (log scale)},
            symbolic x coords={
                Elapsed\ Time,
                DPS,
                User\ CPU,
                System\ CPU,
                Max\ RSS,
                Minor\ PF,
                Major\ PF,
                Voluntary\ CS,
                Involuntary\ CS
            },
            xtick=data,
            x tick label style={rotate=30, anchor=east},
            enlarge x limits=0.05,
            ymajorgrids,
            grid style=dashed,
            legend style={at={(0.5,-0.35)},anchor=north,legend columns=-1},
            nodes near coords,
            every node near coord/.append style={
                font=\tiny,
                rotate=90,
                anchor=west,
                /pgf/number format/.cd, fixed, precision=2
            }
        ]
        % Enclave Run10_SEQ (10 runs avg)
        \addplot[pattern=north east lines,pattern color=black] coordinates {
            (Elapsed\ Time,24.87)
            (DPS,405000)
            (User\ CPU,41.15)
            (System\ CPU,41.00)
            (Max\ RSS,10)
            (Minor\ PF,1)
            (Major\ PF,0.001)
            (Voluntary\ CS,49)
            (Involuntary\ CS,65992)
        };
        % Enclave Run5* (only 2 valid runs avg)
        \addplot[pattern=dots,pattern color=black] coordinates {
            (Elapsed\ Time,24.67)
            (DPS,405500)
            (User\ CPU,41.15)
            (System\ CPU,41.00)
            (Max\ RSS,10)
            (Minor\ PF,1)
            (Major\ PF,0.001)
            (Voluntary\ CS,49)
            (Involuntary\ CS,65992)
        };
        \legend{Enclave Run10\_SEQ, Enclave Run5*}
        \end{axis}
        \end{tikzpicture}
        \caption{Log-scale comparison of Dhrystone Enclave (KE): Run10\_SEQ vs Run5*.\\
        \textit{* Run5 includes only partial runs (others failed).}}
        \label{fig:dhrystone_ke_runs_comparison}
    \end{subfigure}

@@

    % Second Subfigure: Run10_SEQ vs Run5* KE
    \begin{subfigure}{\textwidth}
        \centering
        \begin{tikzpicture}
        \begin{axis}[
            ybar,
            bar width=8pt,
            width=\textwidth,
            height=8cm,
            ymode=log,
            log origin=infty,
            ymin=0.001,
            ylabel={Value (log scale)},
            symbolic x coords={
                Total\ Time,
                Iterations/Sec,
                User\ CPU\ Time,
                System\ CPU\ Time,
                Max\ RSS,
                Minor\ PF,
                Major\ PF,
                Voluntary\ CS,
                Involuntary\ CS
            },
            xtick=data,
            x tick label style={rotate=30, anchor=east},
            enlarge x limits=0.05,
            ymajorgrids,
            grid style=dashed,
            legend style={at={(0.5,-0.35)},anchor=north,legend columns=-1},
            nodes near coords,
            every node near coord/.append style={
                font=\tiny,
                rotate=90,
                anchor=west,
                /pgf/number format/.cd, fixed, precision=2
            }
        ]
        % Run10_SEQ (10 completed runs)
        \addplot[pattern=north east lines,pattern color=black] coordinates {
            (Total\ Time,107.43)
            (Iterations/Sec,929.56)
            (User\ CPU\ Time,41.16)
            (System\ CPU\ Time,41.00)
            (Max\ RSS,10)
            (Minor\ PF,1)
            (Major\ PF,0.001)
            (Voluntary\ CS,49)
            (Involuntary\ CS,65992)
        };
        % Run5* (3/5 completed runs, 2 failed)
        \addplot[pattern=dots,pattern color=black] coordinates {
            (Total\ Time,106.48)
            (Iterations/Sec,939.16)
            (User\ CPU\ Time,41.16)
            (System\ CPU\ Time,41.00)
            (Max\ RSS,10)
            (Minor\ PF,1)
            (Major\ PF,0.001)
            (Voluntary\ CS,49)
            (Involuntary\ CS,65992)
        };
        \legend{Run10\_SEQ, Run5*}
        \end{axis}
        \end{tikzpicture}
        \caption{Log-scale comparison of CoreMark Enclave (KE) performance: Run10\_SEQ vs Run5*.\\
        \textit{* Run5 includes only 3 out of 5 completed runs. Runs 4 and 5 failed.}}
        \label{fig:coremark_ke_runs_comparison}
    \end{subfigure}
\end{figure}

@@

As shown in Figure~\ref{fig:anova-kruskal}, none of the $p$-values from either ANOVA or Kruskal--Wallis testing fell below the $\alpha = 0.05$ significance threshold. This indicates a lack of statistically significant performance variation across hardware scaling steps for all workloads tested. The $R^2$ values in subfigure~\ref{fig:r2_grouped} support this, with low model fit observed in both linear and Random Forest regressions, suggesting weak or no explanatory power.

>>>>

Each benchmark was executed both \emph{sequentially} and \emph{in parallel}, ten times each, allowing us to evaluate both baseline performance and parallel scalability, while repeated runs improve statistical reliability and reduce the influence of outliers.

%The sequential runs (denoted \texttt{Run10\_SEQ}) executed a single instance of the workload in isolation, while the parallel runs (denoted \texttt{Run10}) launched multiple concurrent instances, with results merged to simulate a multi-threaded environment. This dual-mode execution provides insights into how well each workload scales with concurrency, as well as the overheads introduced by context switching and resource contention.
% ------------------------
% Wall-clock time figures
% ------------------------
Figure~\ref{fig:coremark_perf_comparison_log} reports CoreMark's performance profile using the data from Run~10 of both sequential and parallel execution modes. Execution time remained consistent, with the sequential case averaging approximately 101.17 seconds of wall-clock time and the parallel case averaging around 103.37 seconds. This corresponds to an effective throughput of about 988.4 iterations per second for the sequential run and 967.4 iterations per second for the parallel run. User-mode CPU time dominated in both cases (101.20 seconds sequential, 103.39 seconds parallel), accounting for over 99.9\% of total CPU time. System-mode CPU time was negligible (under 0.03 seconds), confirming that the workload’s operational footprint is almost entirely in user space with minimal reliance on system calls or kernel transitions.

\begin{figure}[htbp]
    \centering
    \begin{subfigure}{\textwidth}
        \centering
        \begin{tikzpicture}
        \begin{axis}[
            ybar,
            bar width=8pt,
            width=\textwidth,
            height=8cm,
            ymode=log,
            log origin=infty,
            ymin=0.001,
            ylabel={Value (log scale)},
            symbolic x coords={
                Total\ Time,
                Iterations/Sec,
                User\ CPU\ Time,
                System\ CPU\ Time,
                Max\ RSS,
                Minor\ PF,
                Major\ PF,
                Voluntary\ CS,
                Involuntary\ CS
            },
            xtick=data,
            x tick label style={rotate=30, anchor=east},
            enlarge x limits=0.05,
            ymajorgrids,
            grid style=dashed,
            legend style={at={(0.5,-0.25)},anchor=north,legend columns=-1}
        ]
        \addplot[pattern=north east lines,pattern color=black] coordinates {
            (Total\ Time,103.24)
            (Iterations/Sec,968.64)
            (User\ CPU\ Time,103.26)
            (System\ CPU\ Time,0.02)
            (Max\ RSS,1712.00)
            (Minor\ PF,83.60)
            (Major\ PF,0.20)
            (Voluntary\ CS,0.70)
            (Involuntary\ CS,25815.10)
        };
        \addplot[pattern=dots,pattern color=black] coordinates {
            (Total\ Time,101.11)
            (Iterations/Sec,989.00)
            (User\ CPU\ Time,101.14)
            (System\ CPU\ Time,0.01)
            (Max\ RSS,1691.60)
            (Minor\ PF,83.60)
            (Major\ PF,0.20)
            (Voluntary\ CS,0.90)
            (Involuntary\ CS,350.40)
        };
        \legend{Parallel, Sequential}
        \end{axis}
        \end{tikzpicture}
        \caption{Log‑scale comparison of all key metrics for CoreMark 64M\_1Core: Parallel vs Sequential.}
        \label{fig:coremark_perf_comparison_log}
    \end{subfigure}

@@

    \begin{subfigure}{\textwidth}
        \centering
        \begin{tikzpicture}
        \begin{axis}[
            ybar,
            bar width=8pt,
            width=\textwidth,
            height=8cm,
            ymode=log,
            log origin=infty,
            ymin=0.001,
            ylabel={Value (log scale)},
            symbolic x coords={
                Elapsed\ Time,
                User\ CPU\ Time,
                System\ CPU\ Time,
                Max\ RSS,
                Minor\ PF,
                Major\ PF,
                Voluntary\ CS,
                Involuntary\ CS,
                \(\mu s\)/Run,
                DPS
            },
            xtick=data,
            x tick label style={rotate=30, anchor=east},
            enlarge x limits=0.05,
            ymajorgrids,
            grid style=dashed,
            legend style={at={(0.5,-0.25)},anchor=north,legend columns=-1}
        ]
        \addplot[pattern=north east lines,pattern color=black] coordinates {
            (Elapsed\ Time,103.74)
            (User\ CPU\ Time,11.04)
            (System\ CPU\ Time,0.02)
            (Max\ RSS,1700.00)
            (Minor\ PF,89.60)
            (Major\ PF,0.30)
            (Voluntary\ CS,0.70)
            (Involuntary\ CS,2583.60)
            (\(\mu s\)/Run,10.10)
            (DPS,96478.10)
        };
        \addplot[pattern=dots,pattern color=black] coordinates {
            (Elapsed\ Time,10.02)
            (User\ CPU\ Time,10.03)
            (System\ CPU\ Time,0.01)
            (Max\ RSS,1700.00)
            (Minor\ PF,88.60)
            (Major\ PF,0.10)
            (Voluntary\ CS,0.80)
            (Involuntary\ CS,44.00)
            (\(\mu s\)/Run,0.50)
            (DPS,998646.70)
        };
        \legend{Parallel, Sequential}
        \end{axis}
        \end{tikzpicture}
        \caption{Log‑scale comparison of all key metrics for Dhrystone 64M\_1Core: Parallel vs Sequential.}
        \label{fig:dhrystone_perf_comparison_log}
    \end{subfigure}
    \caption{Comparison of CoreMark and Dhrystone benchmark performance metrics (log-scale) under Parallel and Sequential modes.}
\end{figure}

Memory behavior was stable and well within constraints, with peak resident set size (RSS) at 1692~KB for the sequential run and 1712~KB for the parallel run—both well below the 64~MB memory cap. This indicates that the benchmark’s data and code footprint remained fully cacheable, without triggering paging or dynamic memory expansion. Minor page faults were low and consistent (82--84 for sequential, 82--85 for parallel), though a single major page fault was observed in the parallel run and two in the sequential run, suggesting rare but possible demand paging during lazy allocation. Voluntary context switches were minimal (0--1 sequential, 0--3 parallel), while involuntary context switches showed a stark contrast: approximately 350 in the sequential case versus over 25,800 in the parallel case. This disparity reflects a significantly higher degree of preemption or timer interrupts in the parallel workload environment.

Figure~\ref{fig:dhrystone_perf_comparison_log} presents detailed results from the Dhrystone benchmark under native conditions. The sequential runs exhibited an average elapsed time of approximately 101.2 seconds per run, with user-mode CPU time closely matching this figure, indicating near-total CPU utilization. In contrast, the parallel merged runs completed in roughly 103.4 seconds, with user CPU time again nearly equal to wall-clock time. Throughput, measured in Dhrystone operations per second (DPS), was higher in the sequential case—approximately 988.4~DPS versus 967.4~DPS in the parallel configuration—reflecting slight scheduling overhead from virtual concurrency under QEMU.

Memory footprint remained small (peak RSS ~1.7~MB) and stable, with 82--86 minor page faults per run.

Voluntary context switches were minimal (0--1 sequential, 0--3 parallel), while involuntary context switches showed a stark contrast: approximately 350 in the sequential case versus over 25,800 in the parallel case.

Kyber performance was evaluated using the official \texttt{test\_speed512} binary from the reference implementation's \texttt{ref/} directory.\footnote{See \url{https://github.com/pq-crystals/kyber}. The \texttt{test\_speed512} tool benchmarks key operations using emulated cycle counters in QEMU.} Figure~\ref{fig:kyber_median_cycles_chart_log} presents the median cycle counts for each cryptographic operation, comparing both sequential and parallel enclave execution.

@@

Across all three workloads, cache behavior was stable. QEMU's cache plugin confirmed low instruction and data cache miss rates, reflecting compact memory footprints and tight loop-local access patterns. Instruction streams were \emph{cache-friendly}, thanks to small binaries and predictable control flow, while data cache pressure remained minimal due to static inputs and short-lived stack allocations. This indicates that the workloads are primarily compute-bound rather than memory-bound.

@@

The Dhrystone benchmark demonstrated a similar pattern, with wall-clock times averaging 24.7 seconds under enclave protection, roughly 1.6$\times$ slower than the native 15.3-second average. User and system CPU times both rose to near 41 seconds, reflecting the combined cost of enclave runtime overheads and cryptographic memory protection. Throughput, measured in Dhrystone operations per second, declined modestly to the 395,000--408,000 DPS range from a native baseline near 400,000 DPS. Memory consumption and page fault rates stayed consistent with Kyber’s enclave runs, and involuntary context switch counts remained elevated near 66,000 per run.
\begin{figure}[htbp]
    \centering
    % First Subfigure: Native vs Enclave Run10_SEQ
    \begin{subfigure}{\textwidth}
        \centering
        \begin{tikzpicture}
        \begin{axis}[
            ybar,
            bar width=8pt,
            width=\textwidth,
            height=8cm,
            ymode=log,
            log origin=infty,
            ymin=0.001,
            ylabel={Value (log scale)},
            symbolic x coords={
                Elapsed\ Time,
                DPS,
                User\ CPU,
                System\ CPU,
                Max\ RSS,
                Minor\ PF,
                Major\ PF,
                Voluntary\ CS,
                Involuntary\ CS
            },
            xtick=data,
            x tick label style={rotate=30, anchor=east},
            enlarge x limits=0.05,
            ymajorgrids,
            grid style=dashed,
            legend style={at={(0.5,-0.25)},anchor=north,legend columns=-1},
            nodes near coords,
            every node near coord/.append style={
                font=\tiny,
                rotate=90,
                anchor=west,
                /pgf/number format/.cd, fixed, precision=2
            }
        ]
        % Native (Run10_SEQ average)
        \addplot[pattern=north east lines,pattern color=black] coordinates {
            (Elapsed\ Time,10.02)
            (DPS,995000)
            (User\ CPU,10.05)
            (System\ CPU,0.01)
            (Max\ RSS,1700)
            (Minor\ PF,88.9)
            (Major\ PF,0.1)
            (Voluntary\ CS,0.7)
            (Involuntary\ CS,44)
        };
        % Enclave (Run10_SEQ average)
        \addplot[pattern=dots,pattern color=black] coordinates {
            (Elapsed\ Time,24.87)
            (DPS,405000)
            (User\ CPU,41.15)
            (System\ CPU,41.00)
            (Max\ RSS,10)
            (Minor\ PF,1)
            (Major\ PF,0.001) % avoid log(0)
            (Voluntary\ CS,49)
            (Involuntary\ CS,65992)
        };
        \legend{Native (Sequential), Enclave (Sequential)}
        \end{axis}
        \end{tikzpicture}
        \caption{Log-scale comparison of Dhrystone 64M\_1Core: Native vs Enclave (Sequential).}
        \label{fig:dhrystone_native_vs_enclave_log}
    \end{subfigure}

@@

    % Second Subfigure: Enclave Run10_SEQ vs Run5*
\begin{subfigure}{\textwidth}
    \centering
    \begin{tikzpicture}
    \begin{axis}[
        ybar,
        bar width=8pt,
        width=\textwidth,
        height=8cm,
        ymode=log,
        log origin=infty,
        ymin=0.001,
        ylabel={Value (log scale)},
        symbolic x coords={
            Total\ Time,
            Iterations/Sec,
            User\ CPU\ Time,
            System\ CPU\ Time,
            Max\ RSS,
            Minor\ PF,
            Major\ PF,
            Voluntary\ CS,
            Involuntary\ CS
        },
        xtick=data,
        x tick label style={rotate=30, anchor=east},
        enlarge x limits=0.05,
        ymajorgrids,
        grid style=dashed,
        legend style={at={(0.5,-0.25)},anchor=north,legend columns=-1},
        nodes near coords,
        every node near coord/.append style={
            font=\tiny,
            rotate=90,
            anchor=west,
            /pgf/number format/.cd, fixed, precision=2
        }
    ]
    % Native (Run10_SEQ average)
    \addplot[pattern=north east lines,pattern color=black] coordinates {
        (Total\ Time,100.91)
        (Iterations/Sec,989.80)
        (User\ CPU\ Time,100.99)
        (System\ CPU\ Time,0.013)
        (Max\ RSS,1691.60)
        (Minor\ PF,83.70)
        (Major\ PF,0.20)
        (Voluntary\ CS,0.90)
        (Involuntary\ CS,350.40)
    };
    % Enclave (Run10_SEQ average)
    \addplot[pattern=dots,pattern color=black] coordinates {
        (Total\ Time,107.45)
        (Iterations/Sec,928.97)
        (User\ CPU\ Time,41.16)
        (System\ CPU\ Time,41.00)
        (Max\ RSS,10.00)
        (Minor\ PF,1.00)
        (Major\ PF,0.001) % zero replaced by small non-zero for log scale
        (Voluntary\ CS,49.00)
        (Involuntary\ CS,65992.00)
    };
    \legend{Native (Sequential avg), Enclave (Sequential avg)}
    \end{axis}
    \end{tikzpicture}
    \caption{Log-scale comparison of key metrics for CoreMark 64M\_1Core: Native vs Enclave (averaged over 10 runs).}
    \label{fig:coremark_native_vs_enclave_log}
\end{subfigure}

@@

\begin{figure}[htbp]
    \centering
    % First Subfigure: Native vs Enclave Run10_SEQ
    \begin{subfigure}{\textwidth}
        \centering
        \begin{tikzpicture}
        \begin{axis}[
            ybar,
            bar width=8pt,
            width=\textwidth,
            height=8cm,
            ymode=log,
            log origin=infty,
            ymin=0.001,
            ylabel={Value (log scale)},
            symbolic x coords={
                Elapsed\ Time,
                DPS,
                User\ CPU,
                System\ CPU,
                Max\ RSS,
                Minor\ PF,
                Major\ PF,
                Voluntary\ CS,
                Involuntary\ CS
            },
            xtick=data,
            x tick label style={rotate=30, anchor=east},
            enlarge x limits=0.05,
            ymajorgrids,
            grid style=dashed,
            legend style={at={(0.5,-0.35)},anchor=north,legend columns=-1},
            nodes near coords,
            every node near coord/.append style={
                font=\tiny,
                rotate=90,
                anchor=west,
                /pgf/number format/.cd, fixed, precision=2
            }
        ]
        % Enclave Run10_SEQ (10 runs avg)
        \addplot[pattern=north east lines,pattern color=black] coordinates {
            (Elapsed\ Time,24.87)
            (DPS,405000)
            (User\ CPU,41.15)
            (System\ CPU,41.00)
            (Max\ RSS,10)
            (Minor\ PF,1)
            (Major\ PF,0.001)
            (Voluntary\ CS,49)
            (Involuntary\ CS,65992)
        };
        % Enclave Run5* (only 2 valid runs avg)
        \addplot[pattern=dots,pattern color=black] coordinates {
            (Elapsed\ Time,24.67)
            (DPS,405500)
            (User\ CPU,41.15)
            (System\ CPU,41.00)
            (Max\ RSS,10)
            (Minor\ PF,1)
            (Major\ PF,0.001)
            (Voluntary\ CS,49)
            (Involuntary\ CS,65992)
        };
        \legend{Enclave Run10\_SEQ, Enclave Run5*}
        \end{axis}
        \end{tikzpicture}
        \caption{Log-scale comparison of Dhrystone Enclave: Sequential vs Parallel (5 Runs)*.\\
        \textit{* Run5 includes only partial runs (others failed).}}
        \label{fig:dhrystone_ke_runs_comparison}
    \end{subfigure}

@@

    % Second Subfigure: Run10_SEQ vs Run5* KE
    \begin{subfigure}{\textwidth}
        \centering
        \begin{tikzpicture}
        \begin{axis}[
            ybar,
            bar width=8pt,
            width=\textwidth,
            height=8cm,
            ymode=log,
            log origin=infty,
            ymin=0.001,
            ylabel={Value (log scale)},
            symbolic x coords={
                Total\ Time,
                Iterations/Sec,
                User\ CPU\ Time,
                System\ CPU\ Time,
                Max\ RSS,
                Minor\ PF,
                Major\ PF,
                Voluntary\ CS,
                Involuntary\ CS
            },
            xtick=data,
            x tick label style={rotate=30, anchor=east},
            enlarge x limits=0.05,
            ymajorgrids,
            grid style=dashed,
            legend style={at={(0.5,-0.35)},anchor=north,legend columns=-1},
            nodes near coords,
            every node near coord/.append style={
                font=\tiny,
                rotate=90,
                anchor=west,
                /pgf/number format/.cd, fixed, precision=2
            }
        ]
        % Run10_SEQ (10 completed runs)
        \addplot[pattern=north east lines,pattern color=black] coordinates {
            (Total\ Time,107.43)
            (Iterations/Sec,929.56)
            (User\ CPU\ Time,41.16)
            (System\ CPU\ Time,41.00)
            (Max\ RSS,10)
            (Minor\ PF,1)
            (Major\ PF,0.001)
            (Voluntary\ CS,49)
            (Involuntary\ CS,65992)
        };
        % Run5* (3/5 completed runs, 2 failed)
        \addplot[pattern=dots,pattern color=black] coordinates {
            (Total\ Time,106.48)
            (Iterations/Sec,939.16)
            (User\ CPU\ Time,41.16)
            (System\ CPU\ Time,41.00)
            (Max\ RSS,10)
            (Minor\ PF,1)
            (Major\ PF,0.001)
            (Voluntary\ CS,49)
            (Involuntary\ CS,65992)
        };
        \legend{Run10\_SEQ, Run5*}
        \end{axis}
        \end{tikzpicture}
        \caption{Log-scale comparison of CoreMark Enclave performance: Sequential vs Parallel (5 Runs)*.\\
        \textit{* Run5 includes only 3 out of 5 completed runs. Runs 4 and 5 failed.}}
        \label{fig:coremark_ke_runs_comparison}
    \end{subfigure}
\end{figure}

@@

As shown in Figure~\ref{fig:anova-kruskal}, none of the $p$-values from ANOVA or Kruskal--Wallis testing fell below $\alpha = 0.05$, indicating no statistically significant performance variation across hardware scaling steps. The $R^2$ values in subfigure~\ref{fig:r2_grouped} support this, with low fit in both linear and Random Forest regressions, suggesting weak or no explanatory power.
